---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hmstimer

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.com/poissonconsulting/hmstimer.svg?branch=master)](https://travis-ci.com/poissonconsulting/hmstimer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/hmstimer?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/hmstimer)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/hmstimer/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/hmstimer?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![tinyverse status](https://tinyverse.netlify.com/badge/hmstimer)](https://CRAN.R-project.org/package=hmstimer)
[![CRAN status](https://www.r-pkg.org/badges/version/hmstimer)](https://cran.r-project.org/package=hmstimer)
![CRAN Downloads](http://cranlogs.r-pkg.org/badges/hmstimer)
<!-- badges: end -->

`hmstimer` is an R package to 
track elapsed clock time using a [hms()](https://github.com/tidyverse/hms) scalar (inherits from difftime() with seconds as the unit).

```{r}
library(hmstimer)

t <- tmr_timer()

tmr_elapsed(t)

library(hms) # for prettier printing load hms

tmr_elapsed(t)

t <- tmr_start(t)

tmr_elapsed(t)
tmr_elapsed(t)
t <- tmr_stop(t)

# time elapsed is now fixed
tmr_elapsed(t)
tmr_elapsed(t)

# the timer can be restarted
t <- tmr_start(t)
tmr_elapsed(t)
```

## Installation

To install the latest release version from [CRAN](https://cran.r-project.org)
```
install.packages("hmstimer")
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/hmstimer)
```
if(!"devtools" %in% installed.packages()[,1]) 
  install.packages("devtools")
devtools::install_github("poissonconsulting/hmstimer")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
if(!"drat" %in% installed.packages()[,1]) 
  install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("hmstimer")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/hmstimer/issues).

[Pull requests](https://github.com/poissonconsulting/hmstimer/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
